Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-14 ipsj/paper.tex
Add TLSF+TECS's use cases

>>>>

\subsubsection{Multiple RiteVM}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
    \caption{Component description of RiteVM and TLSF+TECS}
    \label{fig:UseCase_mruby}
\end{figure}

The proposed framework uses TLSF memory allocator for memory management of RiteVMs.
However, since the existing TLSF is not thread-safe, if memory is allocated or deallocated from multiple, memory contention will occur.
As a RiteVM allocates and deallocates memory at high frequency, the memory contention immediately occurs in the case of multiple VMs.

The TLSF components are connected to the RiteVMs to hold its own heap area in each RiteVM as shown in Fig.\ref{fig:UseCase_mruby}.
Since each TLSF component holds a memory pool, multiple RiteVMs can be executed without memory contention.
Fig.\ref{fig:UseCase_mruby} shows that the first RiteVM has a heap area of 1 MB (1024*1024) and the second VM has a heap area of 2 MB (2*1024*1024).
It is easy to set different heap areas in each RiteVM.
In addition, RiteVM performs incremental GC (Garbage Collection), and a VM that started GC does not disturb the execution of other VMs by running GC.

\subsubsection{Memory management for data sending and receiving}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
    \caption{Fixed-size and TLSF memory allocator components}
    \label{fig:UseCase_TINET}
\end{figure}

In TCP/IP protocol stack, memory allocation and release are repeated in each layer such as TCP layer, IP layer, and Ethernet layer, so the role of allocator is important.
TINET+TECS combines all components that manage memory with the allocator.
The TLSF memory allocator can execute at the same speed as compared with the fixed-size memory allocator which TOPPERS/ASP3 supports as standard, and can improve the memory efficiency.
In addition, as shown in Fig.\ref{fig:UseCase_TINET}, the fixed-size memory allocator needs to prepare memory pools of different sizes, and select a memory pool as necessary.
TLSF+TECS efficiently manages the memory without selecting a memory pool.
Since TINET+TECS is component-based system, TLSF+TECS can be easily extended to TINET+TECS.
